Macroscopic Salt Rejection through Electrostatically Gated Porous Graphene

### 2019-01-11 paper/paper.tex
fix typo in name
Implement changes from Roman to manuscript

\author{Roman M. Wyss} \affiliation{Soft Materials,
  Department of Materials, Eidgenössische Technische
  Hochschule (ETH) Zürich, Vladimir-Prelog-Weg 1-5, Zürich CH-8093,
  Switzerland.  }
\altaffiliation{R. M. S. and T. T. contributed equally to this work}
\author{Tian Tian} \affiliation{Institute for
  Chemical and Bioengineering Department of Chemistry and Applied
  Biosciences, Eidgenössische Technische Hochschule (ETH) Zürich,
  Vladimir-Prelog-Weg 1-5, Zürich CH-8093, Switzerland.}
\altaffiliation{R. M. S. and T. T. contributed equally to this work}

@@

\Fig{} \ref{fig:1}a depicts the experimental setup characterizing
ionic diffusion through a sheet of double layer porous graphene
(PG). Two reservoirs, namely the high-concentration reservoir (HCR)
containing electrolyte solution with molar concentration $c_0$, and
the low-concentration reservoir (LCR) containing de-ionized (DI)
water, are separated by a PG membrane supported by polycarbonate
track-etched (PCTE) film. Magnetic stirrers are used to minimize the
effects of external concentration polarization, and a conductivity
probe is placed in the LCR to monitor the ionic concentration as a
function of time. The membrane is attached to a piece of copper tape
connected to a voltage source applying an electrical bias
$V_{\mathrm{G}}$, with the LCR grounded (\Fig{} \ref{fig:1}a
inset). We fabricated the PCTE-supported PG using the protocol
developed by our group \cite{Choi_2018}, as schematically shown in
\Fig{} \ref{fig:1}b. The normally distributed, circular pores with
pore diameters of 20$\pm$10 nm and a pore density of
1.25$\pm$0.25$\times$10$^{10}$ cm$^{-2}$ (\Fig{} \ref{fig:1}c inset) over a
large area were perforated on graphene.  By optimizing the subsequent
transfer process, a high surface coverage ($>$ 98\%) of PG on PCTE was
obtained (\Fig{} \ref{fig:1}c), allowing reliable characterization of
the ion transport behavior (details see Supplementary 
Section \ref{SI-sec:exp}).  The system presented here allows us to systematically
investigate the diffusive flux of ions across a sheet of PG,
$\boldsymbol{J}$, driven by the gradient of electrochemical potential
in the electrolyte medium.

@@

Next, we carried out the same experiments using the PG-covered PCTE
membrane (PG-PCTE), without electrostatic gating. The measured
diffusive flux values, $\boldsymbol{J}_{\mathrm{PG0}}$ (green bars in
\Fig{} \ref{fig:2}b), remain at the same order of magnitude compared
with those of bare PCTE membrane, suggesting that the transport
resistance of PCTE $R_{\mathrm{PCTE}}$, is dominant over that of PG
without gating, $R_{\mathrm{G}}^{0}$. Using a simple circuit model, we
estimate the ratio $\delta$ between $R_{\mathrm{G}}^{0}$ and
$R_{\mathrm{PCTE}}$, such that
$\delta = R_{\mathrm{PCTE}}/R_{\mathrm{G}}^{0}$, to be ~2, which is in
good agreement with the value derived from the experimental data in
\Fig{} \ref{fig:2}b (details see Supplementary Section
\ref{SI-sec:R-model}).
\todo[inline]{Make sure that the values used
  are correct.}

@@

We next discuss the effects of electrostatic gating on graphene. In
order to avoid any interference from the conductivity probe to the
membrane potential, the “three-interval” method, which has been used
in controlling the membrane potential in mesoporous carbon membranes
\cite{Surwade_2014}, is adopted here. \Fig{} \ref{fig:2}a
illustratively represents how the measured conductivity evolves with
time. Specifically, in the first interval, the gate voltage source is
turned off and the conductivity probe is on, allowing us to obtain the
conductivity-time profile with an average slope $s_{1}$ that
corresponds to the diffusive flux across the PG-PCTE membrane. In the
second interval, a voltage $V_{\mathrm{G}}$ is applied to the membrane
after turning off the conductivity probe, followed by the third
interval $s_{3}$, in which the conductivity probe is turned on again
to give the corresponding slope. A control experiment was performed to
ensure the copper tape was not in direct contact with the ionic
solution (Supplementary Section \ref{SI-sec:copper}). The slope corresponding to the
second interval $s_{2}$, as the conductivity probe is off, is
determined by linear interpolation of the conductivities from the
endpoint of interval 1 to the starting point of interval 3. A decrease
of slope observed in interval 2 indicates that the total flux through
PG-PCTE is reduced upon gating (i.e. salt penetration through the PG
pores is partially rejected). We define such experimentally measured
reduction rate as $\eta$, which is equivalent to the decrease of total
diffusive flux through PG-PCTE as follows:
\begin{equation}
  \label{eq:rejection}
  \eta = \frac{\bar{s} - s_{2}}{\bar{s}} = \frac{\boldsymbol{J}_{\mathrm{PG0}}
    - \boldsymbol{J}_{\mathrm{PG}}(V_{\mathrm{G}})}{\boldsymbol{J}_{\mathrm{PG0}}}
\end{equation}
where $\bar{s}$ is the average slope of $s_{1}$ and $s_{3}$, namely
$(s_{1} + s_{3})/2$, and
$\boldsymbol{J}_{\mathrm{PG}}(V_{\mathrm{G}})$ is the diffusive flux
across the PTCE-supported PG double layer as a function of
$V_{\mathrm{G}}$. PG and PCTE membranes effectively form a transport
system with series resistance $R_{\mathrm{PG}}$ (tunable by
$V_{\mathrm{G}}$) and $R_{\mathrm{PCTE}}$ (independent of
$V_{\mathrm{G}}$), respectively. Due to the dominance of
$R_{\mathrm{PCTE}}$ in the ionic transport, significant reduction of
total ionic flux can only be achieved, when
$R_{\mathrm{\mathrm{G}}}(V_{\mathrm{G}} \neq 0) \gg
R_{\mathrm{\mathrm{G}}}^{0}$. Using the circuit analog model, we can
extract the effective salt rejection ratio of PG $\xi$ from the
observable flux reduction ratio $\eta$, as a function of
$V_{\mathrm{G}}$ as (details see Supplementary Section
\ref{SI-sec:R-model}):
\begin{equation}
\label{eq:xi-def}
\xi = \frac{(\delta+1) \eta}{\delta \eta + 1}
\end{equation}
The factor $\xi$ enables a reliable and stable measurement of salt
rejection through the PG membrane, as the salt species and initial
conditions may induce a degree of measurement uncertainty between
different samples.

@@

The above mechanistic findings, nevertheless, do not fully clarify the
experimentally observed reduction of diffusive flux upon
gating. Indeed, the same physical mechanism also governs the ionic
transport through an IFET, in which a nonzero electric potential at
the nanopore center usually results in an increase of ionic
conductivity \cite{Nam_2009,Lee_2015,Feng_2016}. To this end, we
further increased the graphene surface potential $\psi_{\mathrm{G}}$
considering the same system (details see Supplementary Section
\ref{SI-sec:simu-res}). Intriguingly, by increasing $\psi_{\mathrm{G}}$
larger than 400 mV, the ionic flux starts to increase, reversing the
trend observed at the low $\psi_{\mathrm{G}}$ regime, due to (i) the
drift flux become dominant over diffusion flux and (ii) the
concentration near the pore edge (prefered path) greatly increases
(details see Supplementary Section \ref{SI-sec:simu-res}, Supplementary
Figs. \ref{SI-fig:reverse} and \ref{SI-fig:large-V}). This level of
$\psi_{\mathrm{G}}$ cannot be reached experimentally in graphene
membrane, as this requires a $V_{\mathrm{G}}$ larger than 2.0 V, which
triggers the electrochemical reactions \cite{Toh_2011}. On the other
hand, in an IFET, the electric potential on the pore wall is
considerably higher, equivalent to $V_{\mathrm{G}}$ due to the
metallic nature of gate electrode (having an infinitely-large quantum
capacitance). We therefore conclude that the quantum
capacitance-induced nonlinear damping in the surface potential results
in the observed salt rejection.  Following the above discussions, we
further investigate the physical limits for the biased graphene
nanopores. Specifically, the salt rejection characteristics are
controlled by: (i) the overlap of EDL inside the nanopore, essentially
controlled by two length scales of $\lambda_{\mathrm{D}}$ and
$r_{\mathrm{G}}$, and (ii) the graphene surface potential
$\psi_{\mathrm{G}}$ controlled by $V_{\mathrm{G}}$ following
Eq. \eqref{eq:Vg}. To this end, we calculate $\psi_{\mathrm{G}}$ as a
function of $\lambda_{\mathrm{D}} / r_{\mathrm{G}}$ and
$V_{\mathrm{G}}$ (\Fig{} \ref{fig:5}a). Clearly, when the bulk
concentration $c_{0}$ increases, a higher $V_{\mathrm{G}}$ is required
to reach the same level of $\psi_{\mathrm{G}}$. Consequently, as
revealed in \Fig{} \ref{fig:5}b, the calculated salt rejection factor
$\xi$ increases with both $\lambda_{\mathrm{D}} / r_{\mathrm{G}}$ and
$V_{\mathrm{G}}$, in line with the experimentally observed
$\xi - c_{0}$ dependence. We also find the overall trends for
$\psi_{\mathrm{G}}$ and $\xi$ with respect to
$\lambda_{\mathrm{D}}/r_{\mathrm{G}}$ and $V_{\mathrm{G}}$ are very
similar. More importantly, based on our theoretical prediction, with
$V_{\mathrm{G}}$ = 1.25 V and $\lambda_{\mathrm{D}} / r_{\mathrm{G}}$
= 1.0, a high value of $\xi$ of $>$ 0.85 can be achieved.

As seen in the introduction, the diffusive transport resistance of ungated patterned graphene 
is much smaller than that of the PCTE. When gating the graphene membrane,
the overall flux, however, reduces to $\sim$ 55 $\%$
of the ungated flux. This indicates, that R$_{graphene}$ $\approx$ R$_{PCTE}$, 
a 26 fold increase of the resistance with respect to the ungated case. 
This finding indicates, that the experimentally observed $\xi$ for graphene alone 
is indeed higher than the 55$\%$, which is observed for the PG-PCTE combined.

@@

Finally, we examine other salt species and compare the degree of salt
rejection between experiments and simulations. \Fig{} \ref{fig:6}a
presents the measured salt rejection $\xi$ as a function of
$V_{\mathrm{G}}$ at $c_{0}$ = 0.1 mM, for the seven salt species
considered here, including NaCl, LiCl, KCl, MgSO$_{4}$, CaCl$_{2}$,
K$_{2}$SO$_{4}$, and K$_{3}$[Fe(CN)$_{6}$] (details see Supplementary
Section \ref{SI-sec:simu-res}). Similar to the KCl system discussed
earlier, the salt rejection is more pronounced in the positive
$V_{\mathrm{G}}$ regime. The degree of salt rejection deceases with
the salt valance; for example, the measured $\xi$ values at
$V_{\mathrm{G}}$ = 1.25 V decreases from $>$ 0.5 for monovalent NaCl
to -0.04 for multivalent K$_{3}$[Fe(CN)$_{6}$]. This observation is
endorsed by our simulations, in which we calculate $\xi$ as a function
of $V_{\mathrm{g}}$ using the same simulation setups(\Fig{}
\ref{fig:6}b). The calculated $\xi_{\mathrm{max}}$ values are
quantitatively compared with experiments (\Fig{} \ref{fig:6}c), and
the same trend is observed. Indeed, because the Debye length
$\lambda_{\mathrm{D}}$ decreases with the salt valence, the graphene
surface potential appears to decrease in the multivalent salt systems,
thereby reducing $\xi$ (see \Fig{} \ref{fig:5}b). The calculated and
experimental $\xi_{\mathrm{max}}$ as a function of
$\lambda_{\mathrm{D}}$ are consequently plotted, for the seven salt
species considered here (\Fig{} \ref{fig:6}d). Similar to the
experimenal observations, small difference between the $\xi$ of salts
with same valence (e.g. LiCl, NaCl and KCl) is also predicted from the
simulations due to the variation in ionic mobilities. We notice that
without any fitting parameters, our theory can predict the
experimental values reasonably well.  In addition, the
$\xi_{\mathrm{max}}-\lambda_{\mathrm{D}}$ dependence is approximately
linear, suggesting that the effect of Debye length is dominant over
the salt diffusivity. This finding also explains the concentration
dependence of $\xi_{\mathrm{max}}$ observed in \Fig{} \ref{fig:2}d, as
$\lambda_{\mathrm{D}} \propto c_{0}^{-0.5}$. Further including the
specific interaction of ionic species with the graphene membrane
\cite{Ghosh_2018} may give even better agreement with experimental
results.

In summary, we have presented a comparative experimental and modeling
study on macroscopic salt rejection through a sheet of large-area
porous graphene under electrostatic gating. We show that due to a
small quantum capacitance of atomically-thin graphene, the graphene
surface potential is considerably lower than the applied gate
voltage. As a result, the subtle redistribution of the electrochemical
potentials create new pathways for ionic transport, which in turn lead
to a considerable degree of salt rejection. We report a high degree of
salt rejection at $V_{\mathrm{G}}$ = 1.25 V of up to 55\% and 85\%,
based on our experiments and theoretical predictions, respectively. We
demonstrate that the observed salt rejection positively correlates
with the Debye length that nonlinearly modulates the graphene surface
potential and charge density. The experimental results and fundamental
principles presented here open an avenue towards realization of
atomically thin 2D porous membranes for advanced separation process in
electrolyte solutions.

>>>>

\author{Roman M. Wyss} \affiliation{Soft Materials,
  Department of Materials, Eidgenössische Technische
  Hochschule (ETH) Zürich, Vladimir-Prelog-Weg 1-5, Zürich CH-8093,
  Switzerland.  }
\altaffiliation{R. M. W. and T. T. contributed equally to this work}
\author{Tian Tian} \affiliation{Institute for
  Chemical and Bioengineering Department of Chemistry and Applied
  Biosciences, Eidgenössische Technische Hochschule (ETH) Zürich,
  Vladimir-Prelog-Weg 1-5, Zürich CH-8093, Switzerland.}
\altaffiliation{R. M. W. and T. T. contributed equally to this work}

@@

\Fig{} \ref{fig:1}a depicts the experimental setup characterizing
ionic diffusion through a sheet of double layer porous graphene
(PG). Two reservoirs, namely the high-concentration reservoir (HCR)
containing electrolyte solution with molar concentration $c_0$, and
the low-concentration reservoir (LCR) containing de-ionized (DI)
water, are separated by a PG membrane supported by a polycarbonate
track-etched (PCTE) film. Magnetic stirrers are used to minimize the
effects of external concentration polarization, and a conductivity
probe is placed in the LCR to monitor the ionic concentration as a
function of time. The membrane is attached to a piece of copper tape
connected to a voltage source applying an electrical bias
$V_{\mathrm{G}}$, with the LCR grounded (\Fig{} \ref{fig:1}a
inset). We fabricated the PCTE-supported PG as schematically shown in
\Fig{} \ref{fig:1}b, using the protocol developed by our group
\cite{Choi_2018} (details see Supplementary Section
\ref{SI-sec:exp}). The normally distributed, circular pores with pore
diameters of 20$\pm$10 nm and a pore density of
1.25$\pm$0.25$\times$10$^{10}$ cm$^{-2}$ (\Fig{} \ref{fig:1}c inset)
over a large area were perforated on graphene.  By optimizing the
subsequent transfer process, a high surface coverage ($>$ 98\%) of PG
on PCTE was obtained (\Fig{} \ref{fig:1}c), allowing reliable
characterization of the ion transport behavior (details see
Supplementary Section \ref{SI-sec:exp}).  The system presented here
allows us to systematically investigate the diffusive flux of ions
across a sheet of PG, $\boldsymbol{J}$, driven by the gradient of
electrochemical potential in the electrolyte medium.

@@

Next, we carried out the same experiments using the PG-covered PCTE
membrane (PG-PCTE), without electrostatic gating. The measured
diffusive flux values, $\boldsymbol{J}_{\mathrm{PG0}}$ (green bars in
\Fig{} \ref{fig:2}b), remain at the same order of magnitude compared
with those of bare PCTE membrane, suggesting that the transport
resistance of PCTE $R_{\mathrm{PCTE}}$, is dominant over that of PG
without gating, $R_{\mathrm{G}}^{0}$. Using a simple circuit model, we
estimate the ratio $\delta$ between $R_{\mathrm{G}}^{0}$ and
$R_{\mathrm{PCTE}}$, such that
$\delta = R_{\mathrm{PCTE}}/R_{\mathrm{G}}^{0}$, to be $\sim$2.2,
which is in good agreement with the value derived from the
experimental data in \Fig{} \ref{fig:2}b (details see Supplementary
Section \ref{SI-sec:R-model}).  \todo[inline]{Make sure that the
  values used are correct.}

@@

We next discuss the effects of electrostatic gating on graphene. In
order to avoid any interference from the conductivity probe to the
membrane potential, the “three-interval” method, which has been used
in controlling the membrane potential in mesoporous carbon membranes
\cite{Surwade_2014}, is adopted here. \Fig{} \ref{fig:2}a
illustratively represents how the measured conductivity evolves with
time. Specifically, in the first interval, the gate voltage source is
turned off and the conductivity probe is on, allowing us to obtain the
conductivity-time profile with an average slope $s_{1}$ that
corresponds to the diffusive flux across the PG-PCTE membrane. In the
second interval, a voltage $V_{\mathrm{G}}$ is applied to the membrane
after turning off the conductivity probe, followed by the third
interval $s_{3}$, in which the conductivity probe is turned on again
to give the corresponding slope. A control experiment was performed to
ensure the copper tape was not in direct contact with the ionic
solution (Supplementary Section \ref{SI-sec:copper}). The slope
corresponding to the second interval $s_{2}$, as the conductivity
probe is off, is determined by linear interpolation of the
conductivities from the endpoint of interval 1 to the starting point
of interval 3. A decrease of slope observed in interval 2 indicates
that the total flux through PG-PCTE is reduced upon gating (i.e. salt
penetration through the PG pores is hindered). We define such
experimentally measured reduction rate as $\eta$, which is equivalent
to the decrease of total diffusive flux through PG-PCTE as follows:
\begin{equation}
  \label{eq:rejection}
  \eta = \frac{\bar{s} - s_{2}}{\bar{s}} = \frac{\boldsymbol{J}_{\mathrm{PG0}}
    - \boldsymbol{J}_{\mathrm{PG}}(V_{\mathrm{G}})}{\boldsymbol{J}_{\mathrm{PG0}}}
\end{equation}
where $\bar{s}$ is the average slope of $s_{1}$ and $s_{3}$, namely
$(s_{1} + s_{3})/2$, and
$\boldsymbol{J}_{\mathrm{PG}}(V_{\mathrm{G}})$ is the diffusive flux
across the PTCE-supported PG double layer as a function of
$V_{\mathrm{G}}$. PG and PCTE membranes effectively form a transport
system with series resistance $R_{\mathrm{PG}}$ (tunable by
$V_{\mathrm{G}}$) and $R_{\mathrm{PCTE}}$ (independent of
$V_{\mathrm{G}}$), respectively. Due to the dominance of
$R_{\mathrm{PCTE}}$ in the ionic transport, significant reduction of
total ionic flux can only be achieved, when
$R_{\mathrm{\mathrm{G}}}(V_{\mathrm{G}} \neq 0) \gg
R_{\mathrm{\mathrm{G}}}^{0}$. Using the circuit analog model, we can
extract the effective salt rejection ratio of PG $\xi$, defined as
$1 - R_{\mathrm{G}}^{0}/R_{\mathrm{G}}$ from the observable flux reduction ratio $\eta$ (see Supplementary
\Fig{} \ref{SI-fig:eta-all}), as a function of $V_{\mathrm{G}}$ as
(details see Supplementary Section \ref{SI-sec:R-model}):
\begin{equation}
\label{eq:xi-def}
\xi = \frac{(\delta+1) \eta}{\delta \eta + 1}
\end{equation}
The factor $\xi$ is a reliable and stable measure of salt rejection
through the PG membrane upon gating, as the salt species and initial
conditions may induce a degree of measurement uncertainty between
different samples.

@@

The above mechanistic findings, nevertheless, do not fully clarify the
experimentally observed reduction of diffusive flux upon
gating. Indeed, the same physical mechanism also governs the ionic
transport through an IFET, in which a nonzero electric potential at
the nanopore center usually results in an increase of ionic
conductivity \cite{Nam_2009,Lee_2015,Feng_2016}. To this end, we
further increased the graphene surface potential $\psi_{\mathrm{G}}$
considering the same system (details see Supplementary Section
\ref{SI-sec:simu-res}). Intriguingly, by increasing $\psi_{\mathrm{G}}$
larger than 400 mV, the ionic flux starts to increase, reversing the
trend observed at the low $\psi_{\mathrm{G}}$ regime, due to (i) the
drift flux become dominant over diffusion flux and (ii) the
concentration near the pore edge (prefered path) greatly increases
(details see Supplementary Section \ref{SI-sec:simu-res}, Supplementary
Figs. \ref{SI-fig:reverse} and \ref{SI-fig:large-V}). This level of
$\psi_{\mathrm{G}}$ cannot be reached experimentally in graphene
membrane, as this requires a $V_{\mathrm{G}}$ larger than 2.0 V, which
triggers the electrochemical reactions \cite{Toh_2011}. On the other
hand, in an IFET, the electric potential on the pore wall is
considerably higher, equivalent to $V_{\mathrm{G}}$ due to the
metallic nature of gate electrode (having an infinitely-large quantum
capacitance). We therefore conclude that the quantum
capacitance-induced nonlinear damping in the surface potential results
in the observed salt rejection.  Following the above discussions, we
further investigate the physical limits for the biased graphene
nanopores. Specifically, the salt rejection characteristics are
controlled by: (i) the overlap of EDL inside the nanopore, essentially
controlled by two length scales of $\lambda_{\mathrm{D}}$ and
$r_{\mathrm{G}}$, and (ii) the graphene surface potential
$\psi_{\mathrm{G}}$ controlled by $V_{\mathrm{G}}$ following
Eq. \eqref{eq:Vg}. To this end, we calculate $\psi_{\mathrm{G}}$ as a
function of $\lambda_{\mathrm{D}} / r_{\mathrm{G}}$ and
$V_{\mathrm{G}}$ (\Fig{} \ref{fig:5}a). Clearly, when the bulk
concentration $c_{0}$ increases, a higher $V_{\mathrm{G}}$ is required
to reach the same level of $\psi_{\mathrm{G}}$. Consequently, as
revealed in \Fig{} \ref{fig:5}b, the calculated salt rejection factor
$\xi$ increases with both $\lambda_{\mathrm{D}} / r_{\mathrm{G}}$ and
$V_{\mathrm{G}}$, in line with the experimentally observed
$\xi - c_{0}$ dependence. We also find the overall trends for
$\psi_{\mathrm{G}}$ and $\xi$ with respect to
$\lambda_{\mathrm{D}}/r_{\mathrm{G}}$ and $V_{\mathrm{G}}$ are very
similar. More importantly, based on our theoretical prediction, with
$V_{\mathrm{G}}$ = 1.25 V and $\lambda_{\mathrm{D}} / r_{\mathrm{G}}$
= 1.0, a high value of $\xi$ of $>$ 0.9 can be achieved.

% As discussed previously, the diffusive transport resistance of ungated patterned graphene 
% is much smaller than that of the PCTE. When gating the graphene membrane,
% the overall flux, however, reduces to $\sim$ 55 $\%$
% of the ungated flux. This indicates, that R$_{graphene}$ $\approx$ R$_{PCTE}$, 
% a 26 fold increase of the resistance with respect to the ungated case. 
% This finding indicates, that the experimentally observed $\xi$ for graphene alone 
% is indeed higher than the 55$\%$, which is observed for the PG-PCTE combined.

@@

Finally, we examine other salt species and compare the degree of salt
rejection between experiments and simulations. \Fig{} \ref{fig:6}a
presents the measured salt rejection $\xi$ as a function of
$V_{\mathrm{G}}$ at $c_{0}$ = 0.1 mM, for the seven salt species
considered here, including NaCl, LiCl, KCl, MgSO$_{4}$, CaCl$_{2}$,
K$_{2}$SO$_{4}$, and K$_{3}$[Fe(CN)$_{6}$] (details see Supplementary
Section \ref{SI-sec:simu-res}). Similar to the KCl system discussed
earlier, the salt rejection is more pronounced in the positive
$V_{\mathrm{G}}$ regime. The degree of salt rejection deceases with
the salt valance; for example, the measured $\xi$ values at
$V_{\mathrm{G}}$ = 1.25 V decreases from $>$ 0.5 for monovalent NaCl
to -0.04 for multivalent K$_{3}$[Fe(CN)$_{6}$]. This observation is
endorsed by our simulations, in which we calculate $\xi$ as a function
of $V_{\mathrm{g}}$ using the same simulation setups (\Fig{}
\ref{fig:6}b). The calculated $\xi_{\mathrm{max}}$ values are
quantitatively compared with experiments (\Fig{} \ref{fig:6}c), and
the same trend is observed. Indeed, because the Debye length
$\lambda_{\mathrm{D}}$ decreases with the salt valence, the graphene
surface potential appears to decrease in the multivalent salt systems,
thereby reducing $\xi$ (see \Fig{} \ref{fig:5}b). The calculated and
experimental $\xi_{\mathrm{max}}$ as a function of
$\lambda_{\mathrm{D}}$ are consequently plotted, for the seven salt
species considered here (\Fig{} \ref{fig:6}d). Similar to the
experimenal observations, small difference between the $\xi$ of salts
with same valence (e.g. LiCl, NaCl and KCl) is also predicted from the
simulations due to the variation in ionic mobilities. We notice that
without any fitting parameters, our theory can predict the
experimental values reasonably well.  In addition, the
$\xi_{\mathrm{max}}-\lambda_{\mathrm{D}}$ dependence is approximately
linear, suggesting that the effect of Debye length is dominant over
the salt diffusivity. This finding also explains the concentration
dependence of $\xi_{\mathrm{max}}$ observed in \Fig{} \ref{fig:2}d, as
$\lambda_{\mathrm{D}} \propto c_{0}^{-0.5}$. Further including the
specific interaction of ionic species with the graphene membrane
\cite{Ghosh_2018} may give even better agreement with experimental
results.

In summary, we have presented a comparative experimental and modeling
study on macroscopic salt rejection through a sheet of large-area
porous graphene under electrostatic gating. We show that due to a
small quantum capacitance of atomically-thin graphene, the graphene
surface potential is considerably lower than the applied gate
voltage. As a result, the subtle redistribution of the electrochemical
potentials create new pathways for ionic transport, which in turn lead
to a considerable degree of salt rejection. We report a high degree of
salt rejection at $V_{\mathrm{G}}$ = 1.25 V of up to 80\% and 95\%,
based on our experiments and theoretical predictions, respectively. We
demonstrate that the observed salt rejection positively correlates
with the Debye length that nonlinearly modulates the graphene surface
potential and charge density. The experimental results and fundamental
principles presented here open an avenue towards realization of
atomically thin 2D porous membranes for advanced separation process in
electrolyte solutions.
